Solutions to Integer Programming from Quantum Annealing

### 2020-07-12 paper/main.tex
new spectrum plot
update simulator section  in paper

\section{METHODS}
\subsection{Simulation Details}
\subsubsection{The Lindblad Equation}
\label{sec:methods:lindblad}
Say what the simulator is solving
{\color{red} Need to change to talk about full counting statistics.}
{\color{blue}

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
\begin{align}
\label{eq:annealH}
 H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
 +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions. The site dependency takes into account of the annealing offset. $[,]$ denotes the Lie bracket. $L_j$ are the Lindblad operators for decoherence. $\{, \}$ denotes the anti-commutator. In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$. For simplicity we assume all qubits having the same relaxation time. The initial condition is the Gibbs canonical ensemble
\begin{equation}
\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
\end{equation}
where $\beta$ is the inverse temperature.
The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $. Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.

@@

>>>>

\section{METHODS}
\subsection{Simulation Details}
\subsubsection{The Lindblad Equation}
\label{sec:methods:lindblad}
Say what the simulator is solving
{\color{red} Need to change to talk about full counting statistics.}
{\color{red}

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}[\rho (t)] ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
\begin{align}
\label{eq:annealH}
 H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
 +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions. The site dependency takes into account of the annealing offset. $[,]$ denotes the Lie bracket and $\mathcal{L}$ is the Lindblad operator.

For full counting statistics the Lindblad operator is 
\begin{align}
\mathcal{L}[\rho (t)] &=& \Gamma \sum_j   (2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}) \\
&& + e^{-\beta \Delta E_j} (2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} )
\end{align}
where $j$ index the inter-level spacing for energy difference $\Delta E_j$, $\{, \}$ denotes the anti-commutator, $\Gamma = 1/T_c$ is the decoherence rate for coherence time $T_c$.

%In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where

 {\color{blue}
The initial condition is the Gibbs canonical ensemble
\begin{equation}
\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
\end{equation}
where $\beta$ is the inverse temperature.
The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $. Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.

@@

{\color{red}

To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e. $A(s)=A(0)$ and $B(s)=0$. The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$. In this case the analytical solution can be obtained for the wave function oscillation. The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time. For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation. The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./figures/check.png}
	\caption{check}
	\label{fig:check}
\end{figure}
